%% Academic CV for Economics
%% Clean minimal style following standard economics conventions
%% Based on article class with custom formatting

\documentclass[11pt,letterpaper]{article}

% Packages
\usepackage[top=1in,bottom=1in,left=1in,right=1in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{array}

% Hyperlink settings
\hypersetup{
  colorlinks=true,
  linkcolor=blue!70!black,
  urlcolor=blue!70!black,
  citecolor=blue!70!black
}

% Remove paragraph indent, add space between paragraphs
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.4em}

% Custom section formatting
\renewcommand{\section}[1]{%
  \vspace{0.8em}%
  {\large\bfseries\MakeUppercase{#1}}%
  \vspace{0.3em}%
  \hrule%
  \vspace{0.4em}%
}

% Custom compact itemize
\newenvironment{citemize}{%
  \begin{list}{$\cdot$}{%
    \setlength{\leftmargin}{1.5em}%
    \setlength{\itemsep}{0pt}%
    \setlength{\parsep}{0pt}%
    \setlength{\topsep}{0.2em}%
    \setlength{\partopsep}{0pt}%
  }%
}{%
  \end{list}%
}

% Header/footer with name and page numbers
\makeatletter
\def\ps@cvpages{%
  \def\@oddhead{\hfill{\small Ricardo G\'{o}mez-Carrera}\hspace{1em}{\small\thepage}}%
  \def\@evenhead{\hfill{\small Ricardo G\'{o}mez-Carrera}\hspace{1em}{\small\thepage}}%
  \def\@oddfoot{}%
  \def\@evenfoot{}%
}
\def\ps@firstpage{%
  \def\@oddhead{}%
  \def\@evenhead{}%
  \def\@oddfoot{\hfill{\small\thepage}\hfill}%
  \def\@evenfoot{\hfill{\small\thepage}\hfill}%
}
\makeatother

\pagestyle{cvpages}

\begin{document}

\thispagestyle{firstpage}

%% ============================================================
%% HEADER
%% ============================================================

\begin{center}
{\LARGE \textbf{Ricardo G\'{o}mez-Carrera}} \\[0.5em]
Paris School of Economics \\
48 Boulevard Jourdan, 75014 Paris, France \\[0.3em]
Phone: +33 (06) 5114 0100 \quad $\diamond$ \quad
\href{mailto:ricardo.gomez-carrera@psemail.eu}{ricardo.gomez-carrera@psemail.eu} \\
\href{https://ricardogomezcarrera.com/}{ricardogomezcarrera.com} \quad $\diamond$ \quad
\href{https://scholar.google.com/citations?user=X\_RXBoEAAAAJ}{Google Scholar} \quad $\diamond$ \quad
\href{https://www.linkedin.com/in/ricardo-g\%C3\%B3mez-carrera-60849412a/}{LinkedIn} \\[0.3em]
{\small Last updated: May 2026}
\end{center}

\vspace{0.3em}

%% ============================================================
%% EDUCATION
%% ============================================================

\section{Education}

\textbf{Paris School of Economics (PSE)} \hfill Paris, France \\
Ph.D.\ in Economics \hfill Sep.\ 2025--present \\
Master in Applied Economics (PPD), \textit{high honors} \hfill Sep.\ 2024

\textbf{Instituto Tecnol\'{o}gico Aut\'{o}nomo de M\'{e}xico (ITAM)} \hfill Mexico City, Mexico \\
Master in Applied Economics, \textit{highest honors} \hfill Nov.\ 2022 \\
B.A.\ in Economics \hfill Mar.\ 2019

%% ============================================================
%% RESEARCH INTERESTS
%% ============================================================

\section{Research Interests}

Development economics, economics of education, labor economics

%% ============================================================
%% PEER-REVIEWED PUBLICATIONS
%% ============================================================

\section{Peer-Reviewed Publications}

\href{https://doi.org/10.1016/j.latcb.2022.100083}{``Sectoral Supply and Demand Shocks during COVID-19: Evidence from Mexico''} (with Ricardo Chavar\'{i}n and Alfredo Salgado). \textit{Latin American Journal of Central Banking}, 4(1), March 2023.

%% ============================================================
%% BOOKS
%% ============================================================

\section{Books}

\href{https://wir2026.wid.world/}{\textit{World Inequality Report 2026}} (lead author; with Lucas Chancel, Rowaida Moshrif, and Thomas Piketty). World Inequality Lab, December 2025.

\begin{citemize}
  \item Comprehensive analysis of global trends in income, wealth, gender, and environmental inequality, drawing on the work of more than 200 researchers worldwide.
  \item Published in print by \href{https://www.politybooks.com/bookdetail?book\_slug=world-inequality-report-2026--9781509574865}{Polity} (English) and \href{https://www.seuil.com/ouvrage/rapport-sur-les-inegalites-mondiales-2026-lucas-chancel/9782021619676}{Seuil} (French).
  \item Dedicated website: \href{https://wir2026.wid.world/}{wir2026.wid.world} (full report, executive summary, data, and replication materials).
  \item Selected media coverage: \href{https://www.youtube.com/watch?v=WhPHuAA-d0Q}{France 24} (TV), \href{https://www.theguardian.com/inequality/2025/dec/10/just-0001-hold-three-times-the-wealth-of-poorest-half-of-humanity-report-finds}{The Guardian}, \href{https://www.bloomberg.com/news/articles/2025-12-09/world-s-rich-own-triple-the-wealth-of-poorest-half-study-finds}{Bloomberg}, \href{https://www.lemonde.fr/economie/article/2025/12/09/ces-ultrariches-qui-aspirent-une-part-croissante-de-la-richesse-mondiale\_6656576\_3234.html}{Le Monde}, \href{https://elpais.com/economia/2025-12-10/la-brecha-mundial-de-la-desigualdad-se-agranda-el-10-de-la-poblacion-concentra-el-75-del-patrimonio.html}{El Pa\'{i}s}, \href{https://www.aljazeera.com/news/2025/12/10/where-in-the-world-are-wealth-and-income-most-unequal}{Al Jazeera}, \href{https://oglobo.globo.com/economia/noticia/2025/12/09/fatia-dos-10percent-mais-ricos-detem-75percent-da-riqueza-global-e-metade-mais-pobre-fica-com-apenas-2percent-mostra-estudo.ghtml}{O Globo}, \href{https://m.thewire.in/article/political-economy/in-charts-world-inequality-report-2026/amp}{The Wire}, \href{https://savageminds.substack.com/p/ricardo-gomez-carrera}{Savage Minds Podcast}.
\end{citemize}

%% ============================================================
%% WORKING PAPERS
%% ============================================================

\section{Working Papers}

\href{https://ricardogomezcarrera.com/research/working\_papers/Gomez-Carrera%20R.%20%E2%80%93%20From%20Playtime%20to%20Primetime.pdf}{``From Playtime to Primetime: The Medium-term Effects of Compulsory Preschool in Mexico''}.

\href{https://ricardogomezcarrera.com/research/working\_papers/Big\_in\_Health.pdf}{``Going Big in Health: Effect of a Large-Scale Preventive Health Policy''} (with Arturo Aguilar and Adri\'{a}n Rubli).

\href{https://economics.sas.upenn.edu/pier/working-paper/2024/starting-strong-medium-and-longer-run-benefits-mexicos-universal-preschool}{``Starting Strong: Medium- and Longer-run Benefits of Mexico's Universal Preschool Mandate''} (with Jere R.\ Behrman, Susan W.\ Parker, Petra E.\ Todd, and Weilong Zhang).

%% ============================================================
%% TECHNICAL NOTES
%% ============================================================

\section{Technical Notes}

\href{https://wid.world/document/extending-wid-population-series-projections-2024-2100-age-gender-breakdowns-world-inequality-lab-technical-note-2024-12/}{``Extending WID Population Series: Projections 2024--2100, Age \& Gender Breakdowns''}, World Inequality Lab Technical Note 2024/12.

\href{https://wid.world/document/global-inequality-update-2024-technical-note/}{``Global Inequality Update 2024''}, World Inequality Lab Technical Note 2024/11.

\href{https://ricardogomezcarrera.com/research/technical\_notes/Factores\_ciclicos\_banxico.pdf}{``Cyclical and Non-cyclical Factors in the Evolution of Mexico's Labor Participation Rate since 2005''} (with Le\'{o}n Fern\'{a}ndez and Daniel Osuna). Banco de M\'{e}xico, Quarterly Report April--June 2023, Box~3.

%% ============================================================
%% HONORS AND AWARDS
%% ============================================================

\section{Honors and Awards}

\begin{tabular}{@{}lp{0.88\textwidth}@{}}
2025 & \href{https://secihti.mx/becas-al-extranjero/}{SECIHTI Doctoral Fellowship} --- Mexican government fellowship for doctoral studies abroad \\
2025 & \href{https://www.linkedin.com/posts/centre-des-professions-financieres\_36cimef-activity-7325922367442935810-NmD\_}{36th International Master Thesis Competition in Economics and Finance} (honorable mention) \\
2024 & \href{https://agenda.colmex.mx/Actividad/4159/ceremonia-de-entrega-del-premio-de-economia-joaquin-xirau-icaza-2024/20241022}{Joaqu\'{i}n Xirau Icaza Economics Award} (winner) \\
2024 & \href{https://exalumnos.itam.mx/es/noticia/conoce-los-ganadores-del-xxix-premio-de-investigacion-exitam}{XXIX ExITAM Research Award} (honorable mention) \\
2024 & \href{https://www.cemla.org/actividades/2022-final/2022-11-xxvii-meeting-of-the-central\%E2\%80\%93bank\%E2\%80\%93researchers-network.html}{Latin American Journal of Central Banking Special Issue Award} (second place) \\
\end{tabular}

%% ============================================================
%% PRESENTATIONS
%% ============================================================

\section{Presentations}

\textit{Academic Presentations:}

\begin{tabular}{@{}lp{0.85\textwidth}@{}}
2026 & \href{https://www.facebook.com/FEconomiaUNAM/videos/jayati-ghosh-qui\%C3\%A9n-financia-el-bienestar/2205858323588729/}{Keynote Conference by Jayati Ghosh: ``\textquestiondown Qui\'{e}n financia el bienestar?''}, Facultad de Econom\'{i}a, UNAM (invited speaker) \\
2026 & \href{https://sites.google.com/site/doctorissimes3/21st-doctorissimes-2026/}{21st Doctorissimes Conference}, Paris School of Economics (poster) \\
2026 & Casual Friday Development Seminar, Paris School of Economics \\
2026 & \href{https://www.youtube.com/@LSEInequalities}{Inequalities Seminar Series}, International Inequalities Institute, London School of Economics \\
2023 & \href{https://posgrados.itam.mx/es/evento/itam-alumni-conference}{ITAM Alumni Conference}, ITAM \\
\end{tabular}

\vspace{0.3em}

\textit{Policy Presentations:}

\begin{tabular}{@{}lp{0.85\textwidth}@{}}
2026 & Oxfam Mexico -- \href{https://oxfam.mx/enfb-2026/}{First National Meeting on Financing for Welfare (ENFB 2026)}, Mexico City (invited) \\
2026 & United Nations -- \href{https://www.un.org/en/desa}{Department of Economic and Social Affairs} (webinar, invited) \\
2026 & European Parliament -- \href{https://www.europarl.europa.eu/committees/en/empl/home/highlights}{Employment and Social Affairs Committee}, Brussels (invited) \\
2026 & European Commission -- \href{https://commission.europa.eu/about/departments-and-executive-agencies/economic-and-financial-affairs\_en}{DG for Economic and Financial Affairs}, Brussels (invited) \\
2026 & European Commission -- \href{https://commission.europa.eu/about/departments-and-executive-agencies/reform-and-investment-task-force\_en}{Reform and Investment Task Force}, Brussels (invited) \\
\end{tabular}

%% ============================================================
%% REFEREE SERVICE
%% ============================================================

\section{Referee Service}

\textit{Journal of Development Economics}

%% ============================================================
%% MEDIA CONTRIBUTIONS
%% ============================================================

\section{Media Contributions}

\begin{tabular}{@{}ll@{}}
2026 & \href{https://blogs.lse.ac.uk/inequalities/2026/05/12/56000-people-own-three-times-more-wealth-than-half-of-humanity/}{``56,000 People Own Three Times More Wealth Than Half of Humanity''}, LSE Inequalities Blog \\
2026 & \href{https://www.politybooks.com/blog-detail/inequality-is-a-choice-what-the-world-inequality-report-2026-reveals-about-our-economic-moment}{``Inequality Is a Choice. What the WIR Reveals About Our Economic Moment''}, Polity \\
2025 & \href{https://surcos.com.mx/la-desigualdad-no-crece-sola-la-dejamos-crecer/}{``La desigualdad no crece sola. La dejamos crecer''}, Surcos \\
2024 & \href{https://voxdev.org/topic/education/mexicos-preschool-mandate-set-children-succeed}{``Mexico's Preschool Mandate Set Children up to Succeed''}, VoxDev \\
\end{tabular}

%% ============================================================
%% RESEARCH PROFESSIONAL EXPERIENCE
%% ============================================================

\section{Research Professional Experience}

\textbf{World Inequality Lab} \hfill Paris, France \\
\textit{World Inequality Report Coordinator} \hfill Dec.\ 2024--present

\begin{citemize}
  \item Coordinator of the \href{https://wir2026.wid.world/}{World Inequality Report 2026}: global analysis of income, wealth, gender inequality, and environmental impacts.
\end{citemize}

\textit{Economist} \hfill Aug.\ 2024--Nov.\ 2024

\begin{citemize}
  \item Lead author of two technical notes expanding the World Inequality Database with historical and projected population series for 216 countries (1800--2100) and updating global inequality estimates.
\end{citemize}

\textbf{Banco de M\'{e}xico (Central Bank)} \hfill Mexico City, Mexico \\
\textit{Research Economist} \hfill Sep.\ 2020--Sep.\ 2024

\begin{citemize}
  \item Co-authored a published article analyzing supply and demand shocks from COVID-19 on Mexican sectoral activity using sign-restricted SBVAR.
  \item Conducted research on gender gaps in labor force participation, trade integration effects on unemployment, and labor market slack measurement via PCA.
  \item Analyzed private sector expectations data to inform monetary policy research and forecasting.
\end{citemize}

%% ============================================================
%% RESEARCH ASSISTANTSHIPS
%% ============================================================

\section{Research Assistantships}

\textbf{Paris School of Economics} \hfill Paris, France \\
\textit{Research Assistant to Karen Macours} \hfill Sep.\ 2023--Dec.\ 2023

\begin{citemize}
  \item Studied agricultural innovation adoption in Uganda in collaboration with CGIAR and the World Bank.
  \item Contributed to data management, programming, and econometric analysis.
\end{citemize}

\textbf{Center for Economic Research, ITAM} \hfill Mexico City, Mexico \\
\textit{Research Assistant to Arturo Aguilar and Adri\'{a}n Rubli} \hfill Feb.\ 2020--Jan.\ 2022

\begin{citemize}
  \item Co-authored a working paper evaluating a large-scale preventive health policy in Mexico. Promoted from RA to co-author.
\end{citemize}

\textbf{Banco de M\'{e}xico (Central Bank)} \hfill Mexico City, Mexico \\
\textit{Research Assistant to Gabriela L\'{o}pez Noria} \hfill Sep.\ 2020--Sep.\ 2024

\begin{citemize}
  \item Contributed to a \href{https://www.banxico.org.mx/publications-and-press/banco-de-mexico-working-papers/\%7BFE5F557C-DAF1-9E92-0ACA-0312D6BFF8C1\%7D.pdf}{working paper} studying the effects of trade and technology on the Mexican labor market, finding that trade integration reduced unemployment, especially for women.
\end{citemize}

%% ============================================================
%% EXTERNAL CONSULTANTSHIPS
%% ============================================================

\section{External Consultantships}

\textbf{\href{https://www.afd.fr/en/fund-innovation-development-innovating-against-poverty-and-inequality}{Fund for Innovation in Development (FID-AFD)}} \hfill Paris, France \\
\textit{External Consultant} \hfill Feb.\ 2026--present

\begin{citemize}
  \item Research consultancy on innovation against poverty and inequality.
\end{citemize}

\textbf{Inter-American Development Bank (IADB)} \hfill Mexico City, Mexico \\
\textit{External Consultant with Amado Crotte} \hfill May 2019--Oct.\ 2019

\begin{citemize}
  \item Co-authored a working paper on transport policy evaluation using diff-in-diff identification.
\end{citemize}

%% ============================================================
%% OTHER PROFESSIONAL EXPERIENCE
%% ============================================================

\section{Other Professional Experience}

\textbf{Ministry of Finance and Public Credit} \hfill Mexico City, Mexico \\
\textit{Director of Domestic Debt Issuance} \hfill Oct.\ 2019--Jul.\ 2020

\begin{citemize}
  \item Led team of 5; managed domestic debt issuance strategy and mitigated COVID-19 liquidity pressures on Mexican debt markets.
\end{citemize}

\textit{Deputy Director of Public Debt and Infrastructure Projects} \hfill Jun.\ 2017--Sep.\ 2019

\begin{citemize}
  \item Structured transport infrastructure projects, managed the National Infrastructure Fund, and conducted IMF-methodology debt sustainability analysis.
\end{citemize}

\textit{Head of Department of Infrastructure Projects} \hfill Mar.\ 2017--Jun.\ 2017

\begin{citemize}
  \item Evaluated and structured projects in the transport and water sectors.
\end{citemize}

%% ============================================================
%% SKILLS AND LANGUAGES
%% ============================================================

\section{Skills and Languages}

\textbf{Software:} R, Stata, EViews, Matlab, \LaTeX, QGIS, MS Office \\
\textbf{Languages:} Spanish (native), English (fluent; TOEFL 111/120), French (upper intermediate, B2)

%% ============================================================
%% SERVICE
%% ============================================================

\section{Service}

CISV International, Enlace Rural, Colonias de Vacaciones (2011--2018)

\end{document}
